### 2016-07-01 Projects/DelCo_2012/Report/DelCo_2012.tex
add suppression test data to table, cleanup tables to fit on page

\begin{table}[!ht]
\centering
\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel           & Ventilation     \\
\midrule
 1 & CAF~1    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door            \\
 2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
 3 & CAF~2    &  7/8'' Solid Stream &  120~gpm/60~cfm   & Furniture      & Door            \\
 4 & Water~2  &  7/8'' Solid Stream &  120~gpm    		& Furniture      & Door            \\
 5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 6 & CAF~3    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 8 & CAF~4    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
10 & Attic~2  &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
12 & CAF~5    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
14 & CAF~6    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}[!ht]
\centering
\caption{Fire Suppression Results}\label{tab:Test_Results}
\begin{tabular}{lccc}
\toprule[1.5pt]
                 & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	         & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 0.15~m (6~in) Above Floor \\
\midrule
CAF~1 Hallway    & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
CAF~1 Room       & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
Water~1 Hallway  & 770~$^{\circ}$C - 300~$^{\circ}$C   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
Water~1 Room     & 180~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
CAF~2 Hallway    & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~2 Room       & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~2 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
Water~2 Room     & 250~$^{\circ}$C - 50~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~3 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 60~kW/m$^2$ - 10~kW/m$^2$  \\
Water~3 Room     & 260~$^{\circ}$C - 180~$^{\circ}$C   & 90~$^{\circ}$C - 20~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~4 Hallway  & 860~$^{\circ}$C - 430~$^{\circ}$C   & 870~$^{\circ}$C - 210~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
Water~4 Room     & 260~$^{\circ}$C - 160~$^{\circ}$C   & 120~$^{\circ}$C - 50~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
CAF~4 Hallway    & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~5 Hallway  & 820~$^{\circ}$C - 380~$^{\circ}$C   & 420~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
Water~5 Room     & 400~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 90~$^{\circ}$C    & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
CAF~5 Hallway    & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~6 Hallway  & 800~$^{\circ}$C - 150~$^{\circ}$C   & 650~$^{\circ}$C - 20~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
Water~6 Room     & 200~$^{\circ}$C - 90~$^{\circ}$C    & 60~$^{\circ}$C - 40~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
CAF~6 Hallway    & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}[!ht]
\centering
\footnotesize
\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    & Ventilation  \\
\midrule
 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
 39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Double Doors, 1st Floor Door \\
 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 41b & CAF~9     &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 41c & CAF~9b    &  7/8'' Solid Stream  &  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}[!ht]
\centering
\caption{Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
\begin{tabular}{lccc}
\toprule[1.5pt]
           & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	   & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	           & 1~m (3~ft) Above Floor \\
\midrule
CAF~7      & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Class A~1  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\begin{table}[!ht]
\centering
\caption{Single Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel           & Ventilation     \\
\midrule
 1 & CAF~1    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door            \\
 2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
 3 & CAF~2    &  7/8'' Solid Stream &  120~gpm/60~cfm   & Furniture      & Door            \\
 4 & Water~2  &  7/8'' Solid Stream &  120~gpm    		& Furniture      & Door            \\
 5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 6 & CAF~3    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
 8 & CAF~4    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
 9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
10 & Attic~2  &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
12 & CAF~5    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
14 & CAF~6    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}[!ht]
\centering
\caption{Single Story Fire Suppression Results}\label{tab:Test_Results}
\begin{tabular}{lccc}
\toprule[1.5pt]
                 & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	         & 0.3~m Below Ceiling                 & 0.3~m  Above Floor	                 & 0.15~m Above Floor \\
\midrule
CAF~1 Hallway    & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
CAF~1 Room       & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
Water~1 Hallway  & 770~$^{\circ}$C - 300~$^{\circ}$C   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
Water~1 Room     & 180~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
CAF~2 Hallway    & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~2 Room       & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~2 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
Water~2 Room     & 250~$^{\circ}$C - 50~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~3 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 60~kW/m$^2$ - 10~kW/m$^2$  \\
Water~3 Room     & 260~$^{\circ}$C - 180~$^{\circ}$C   & 90~$^{\circ}$C - 20~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~4 Hallway  & 860~$^{\circ}$C - 430~$^{\circ}$C   & 870~$^{\circ}$C - 210~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
Water~4 Room     & 260~$^{\circ}$C - 160~$^{\circ}$C   & 120~$^{\circ}$C - 50~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
CAF~4 Hallway    & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~5 Hallway  & 820~$^{\circ}$C - 380~$^{\circ}$C   & 420~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
Water~5 Room     & 400~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 90~$^{\circ}$C    & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
CAF~5 Hallway    & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
Water~6 Hallway  & 800~$^{\circ}$C - 150~$^{\circ}$C   & 650~$^{\circ}$C - 20~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
Water~6 Room     & 200~$^{\circ}$C - 90~$^{\circ}$C    & 60~$^{\circ}$C - 40~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
CAF~6 Hallway    & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}[!ht]
\centering
\footnotesize
\caption{Two Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    & Ventilation  \\
\midrule
 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Doors, 1st Floor Door \\
 39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Doors, 1st Floor Door \\
 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 40c & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 41b & CAF~9a    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 41c & CAF~9b    &  7/8'' Solid Stream  &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}[!ht]
\centering
\caption{Two Story Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
\begin{tabular}{lcccc}
\toprule[1.5pt]
           &               & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               & 1~m Above Floor \\
\midrule
CAF~7      & 24            & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7    & 29            & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a     & 16            & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b     & 21            & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Water~8    & 18            & 440~$^{\circ}$C - 295~$^{\circ}$C   & 375~$^{\circ}$C - 250~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
Class A~1  & 19            & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a     & 21            & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b     & 16            & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
